Title

### 2022-12-12 Manuscript/Manuscript.Rmd
working introduction

3. The stability of plant's visitation rate is more affected by the asynchrony of pollinator species abundances than by pollinator richness. shows a negative tendency. As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative relation was observed between stability of seed and the stability of visitation rate. However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.

@@

Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2012], the stability of pollinator communities may increase the stability of plant reproductive success. A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013] (Hoehn et al. 2008; Fründ et al. 2010, Albrecht et al. 2012, Blüthgen and Klein, 2013, Fründ et al. 2013). Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] (Pisanty et al. 2016, Rader et al. 2016) and consequently may provide pollination services at different times of the season. 
on the other hand, few studies link the visitation rate directly with plant reproductive but they generally find positive association. Sites with more visitation show higher pollen deposition and fruit set (Garibaldi et al., 2014; Kaiser‐Bunbury et al., 2017).

@@

Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al. 2004; Burd 1994; Knight et al. 2005)
plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al. 2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012)

the occurrence and magnitude of pollen limitation varies among years for individual populations (Burd 1994, Ashman et al. 2004), primarily because of variation in pollinator service (Aizen and Harder 2007).

>>>>

3. The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness. However, we found a strong positive relationship between richness and asynchrony of pollinators. As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate. However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.

@@

Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success. A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013]. Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the season. 
On the other hand, few studies link the visitation rate directly with plant reproductive. In some case, sites with more visitation show higher plant reproductive and in another they do not find relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017). Likewise, in more visited sites, it has been observed lower pollen limitation of fruit set and seed production [(Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013)](). The occurrence and magnitude of pollen limitation can varies among years for individual populations (Burd 1994, Ashman et al. 2004), primarily because of variation in pollinator service (Aizen and Harder 2007).

@@

[?](Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al. 2004; Burd 1994; Knight et al. 2005).plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al. 2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012))
